### 2018-07-05 Thesis/Parts/Future_work/Future_work.tex

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focussed on the quality of word embeddings on academic texts. To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.

@@

\subheader{Pre-categorization}
Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figure~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}). This knowledge could be used to pre-process given texts, creating a two-step search. This method would first categorize the given article into a field, and then search in the limited set of journals for the best fit. This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e. cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity. A possible downside of this approach is the need for data within each domain, since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization. The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions. In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization. The goal is to have multiple separate vector spaces, for this is does not matter if the "domains" are well-interpretable or make sense to humans.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focused on the quality of word embeddings on academic texts. To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.

@@

\subheader{Pre-categorization}
Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figure~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}). This knowledge could be used to pre-process given texts, creating a two-step search. This method would first categorize the given article into a field, and then search in the limited set of journals for the best fit. This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e. cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity. A possible downside of this approach is the need for data within each domain, since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization. The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions. In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization. The goal is to have multiple separate vector spaces, for this it does not matter if the "domains" are well-interpretable or make sense to humans.
\end{document}

### 2018-07-05 Thesis/Parts/Research_results/Research_results.tex

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 7: Discussion.
\subheader{Ranking}
The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
\clearpage
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\end{figure}
\clearpage
\subheader{Rank distribution}
Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The Figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}. The Y-axis of the two Figures show the fraction of the total number of articles. Due to this, all sets will move towards one. When one is hit, the graph stagnates since there are no more articles that can be added once the value reaches one. The X-axis plots the ranks of the articles. These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set}\label{figure:titleDistribution}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
\end{figure}

@@

Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1. We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e. Figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding

@@

Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}. It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that have the journals from which they were taken at rank 0, meaning that the journal has the closest embedding. The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.\\

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 6: Discussion.
\subheader{Ranking}
The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
\clearpage
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\end{figure}
\clearpage
\subheader{Rank distribution}
Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The Figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}. The Y-axis of the two Figures show the fraction of the total number of articles. Due to this, all sets will move towards one. When one is hit, the graph stagnates since there are no more articles that can be added once the value reaches one. The X-axis plots the ranks of the articles. These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set}\label{figure:titleDistribution}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
\end{figure}

@@

Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and F1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1. We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e. Figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding

@@

Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}. It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that their source\footnote{Journal from which the article was taken} journal as first result in the ranking. The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}. Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
